---
title: "Introduction to twitterapiR"
author: "Nelson Tang, Xiang Ling Zou, Nyanda Redwood"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{cnfapi-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup}
library(twitterapiR)
library(dplyr)
library(ggplot2)
```

## Descritpion  
  
The `twitterapiR` package is an R wrapper for [Twitter API](https://developer.twitter.com/en/docs/twitter-api), which provides programmatic access to the popular social media platform **Twitter**. The `twitterapiR` package provides access to each of the endpoints of **Twitter API**, and it  contains several functions, for each of which the following documentation offers usage examples.

## Function Usage
The `searchTweets()` function can be used to find recent tweets using characters including hash tags. In the example below `searchTweets()` function returns all the users who recently used #ubc.

```{r}

set_bearer('Tds7CCMzPsJbRZH7aikpKiObN', 'lPH7pIQIS1pVinxh48xvXWgqzGa9gre4Utb9tIZ2W1U0nSCgrz')
ubc_tweets <- searchTweets("#ubc", resultType = "recent",count = 100)
created_time <- substr(ubc_tweets$created_time, start = 5, stop = 13)
created_time <- strptime(created_time,format='%b %d %H')
created_time_df <- as.data.frame(created_time)

created_time_df <-  created_time_df %>% group_by(created_time) %>% summarize(num_tweets = n())


ggplot(created_time_df, aes(x = created_time, y = num_tweets)) + 
    geom_area(fill="firebrick") +
    geom_line(color="black", size=1) +
    geom_point(color="black", size=3) +
    theme_bw()+
    labs(x = "Created Time", y= "Number of Tweets")+
    ggtitle("The Latest 100 Trending Tweets Containing the Hashtag #ubc")
    theme(panel.grid.major.x = element_blank(),panel.grid.minor.x = element_blank())


```
  
The `followersCount()` function can be used to quickly get the number of followers a user has by using the user's screen name. In the plot below we used this function in a for loop to get the followers of the following state leaders as of 2022:

- Joe Biden -President of the United States
- Justin Trudeau -Prime Minister of Canada
- Boris Johnson -Prime Mnister of the United Kingdom
- Emmanuel Macron -President of France
- Moon Jae-in -President of South Korea
```{r} 
# Use followersCount to find the number of follower for each country leader
list = c("POTUS", "JustinTrudeau", "BorisJohnson", "EmmanuelMacron", "moonriver365")
followers = c()
for (i in list){
    followers[i]=followersCount(screen_name =i)$followers_count
}

followers <- as.data.frame(followers)
followers["name"] <- c("Joe Biden", "Justin Trudeau", "Boris Johnson", "Emmanuel Macron", "Moon Jae-in" )

followers["no_of_followers"] <- followers$followers

followers$followers = NULL

followers






```


```{r}

theme_set(theme_bw())  # pre-set the bw theme.

g <- ggplot(followers, aes(name, no_of_followers))

# barplot
g + geom_col() + 
  labs(subtitle="example plot", 
       y="no of followers", 
       x="name", 
       title="Popular President?", 
       )
```

The `user_friends()` function can be used to quickly get the number of friends a user has by using the user's screen name.  
  
Similar to the above plot, the plot below uses the `user_friends()` function in a for loop to get the friends of the following state leaders as of 2022:

- Joe Biden -President of the United States
- Justin Trudeau -Prime Minister of Canada
- Boris Johnson -Prime Mnister of the United Kingdom
- Emmanuel Macron -President of France
- Moon Jae-in -President of South Korea

```{r}

# Use user_friends to find the number of friends for each country leader
list = c("POTUS", "JustinTrudeau", "BorisJohnson", "EmmanuelMacron", "moonriver365")
friends = c()
for (i in list){
    friends[i]=nrow(user_friends(screen_name=i))
}

friends <- as.data.frame(friends)
friends["name"] <- c("Joe Biden", "Justin Trudeau", "Boris Johnson", "Emmanuel Macron", "Moon Jae-in" )

friends["no_of_friends"] <- friends$friends

friends$friends = NULL

friends
```
```{r}
# load package and data
theme_set(theme_bw())  # pre-set the bw theme.

g <- ggplot(friends, aes(name, no_of_friends))

# barplot
g + geom_col() + 
  labs(subtitle="example plot", 
       y="no of followers", 
       x="name", 
       title="Popular President?", 
       )
```

